Initial Analysis

### 2019-11-06 Initial_Analysis.Rmd
Included some parenthesis in the status species function

  # Get Variables to perform status metric
  Status_Data <- Data %>% 
    anti_join(No_Status_Data, # Removes no status data
              by = c("TaxonKey","Territory")
    ) %>% 
    # Get Max catch and max catch year
    group_by(TaxonKey,Territory) %>% 
    top_n(1,RMean) %>% 
    rename(Max_Peak = RMean,
           Y_Max_Peak = Year) %>% 
    # Get Min catch after peak catch
    left_join(Data,
              by = c("TaxonKey","Territory")
    ) %>% 
    filter(Year > Y_Max_Peak) %>% # Filter years after peak year
    group_by(TaxonKey,Territory) %>% 
    top_n(-1,RMean) %>% # find min value
    rename(Post_Max_Min = RMean,
           Y_Post_Max_Min = Year) %>% 
    left_join(Data,
              by = c("TaxonKey","Territory")
    ) %>% 
    # Final Species Status Evaluation 
    mutate(Status = ifelse(Year > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
                           ifelse((Year < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Year)),"Developing",
                                  ifelse(RMean > Max_Peak*0.50,"Max Exploited",
                                         ifelse(Year > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Over Exploited",
                                                ifelse(Year > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
                                                       "No Status")
                                         )
                                  )
                           )
    )
    ) %>% 
    filter(Year > 2004) %>% # last 10 years of data
    group_by(TaxonKey,Territory,Status) %>% 
    summarise(n_Status= n()) %>% 
    group_by(TaxonKey,Territory) %>% 
    top_n(1,n_Status) %>%
    select(-n_Status)

@@

# Save data
# write.csv(Species_Status,
#           paste(Results_Path,"Species_Status.csv",sep=""),
#                 row.names = F)

@@

# Species list to get species names
Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep=""))
Spp_Clasification <- fread(paste(Data_Path,"Distribution_Data/SppTaxonName.csv",sep=""))

@@

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(Data_Path,"Distribution_Data/Species_Status.csv", sep =""))

@@

length(unique(Total_trans_n$TaxonKey)) #674 spp

@@

Countries_Data_Plot <- Tresholded_T_Data %>% 
  group_by(Territory = CT_fishing_entity) %>% 
  summarise(value = length(unique(TaxonKey))) %>% 
  left_join(UN_Regions, by ="Territory") %>%
  mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
  rename(FishingRegion=Territory) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(individual = fishing_entity,group) %>% 
  summarise(Total_trans = sum(value,na.rm=T)) %>% 
  mutate(value = ifelse(Total_trans > 100,100,Total_trans)) %>% 
  filter(!is.na(individual)) %>% 
  select(individual,group,value) %>% 
  arrange(group,value)

@@

Discrete_Data_Plot <- Tresholded_D_Data %>% 
  summarise(value =sum(value,na.rm = T)*-1) %>% # Multyply them by -1 so they appear negative on plot
  mutate(value = ifelse(value <= -100,-100,value)) %>% 
  left_join(UN_Regions, by ="Territory") %>%
  mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
  filter(!is.na(Territory)) %>% 
  select(individual = Territory,
         group,
         value)

@@

# Include possible missing countries in bothe datasets
Countries_Data_Plot <- Discrete_Data_Plot %>% 
  anti_join(Countries_Data_Plot,
            by = c("individual","group")) %>% 
  mutate(Total_Discrete = 0) %>% 
  bind_rows(Countries_Data_Plot)

Discrete_Data_Plot <- Countries_Data_Plot %>% 
  anti_join(Discrete_Data_Plot,
            by = c("individual","group")) %>% 
  mutate(value = 0) %>% 
  bind_rows(Discrete_Data_Plot)

```{r}

data <- data.frame(
  individual=paste( "Mister ", seq(1,60), sep=""),
  group=c( rep('A', 10), rep('B', 30), rep('C', 14), rep('D', 6)) ,
  value1=sample( seq(10,100), 60, replace=T),
  value2=sample( seq(10,100), 60, replace=T),
  value3=sample( seq(10,100), 60, replace=T)
)

# Transform data in a tidy format (long format)
data <- data %>% gather(key = "observation", value="value", -c(1,2))

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(data$group)*nObsType, ncol(data)) )
colnames(to_add) <- colnames(data)
to_add$group <- rep(levels(data$group), each=empty_bar*nObsType )
data <- rbind(data, to_add)
data <- data %>% arrange(group, individual)
data$id <- rep( seq(1, nrow(data)/nObsType) , each=nObsType)

# Get the name and the y position of each label
label_data <- data %>% group_by(id, individual) %>% summarize(tot=sum(value))
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)

# prepare a data frame for base lines
base_data <- data %>% 
  group_by(group) %>% 
  summarize(start=min(id), end=max(id) - empty_bar) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# Make the plot
ggplot(data) +

  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=observation), stat="identity", alpha=0.5) +
  # scale_fill_viridis(discrete=TRUE) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 150, xend = start, yend = 150), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 200, xend = start, yend = 200), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +

  # Add text showing the value of each 100/75/50/25 lines
  ggplot2::annotate("text", x = rep(max(data$id),5), y = c(0, 50, 100, 150, 200), label = c("0", "50", "100", "150", "200") , color="grey", size=6 , angle=0, fontface="bold", hjust=1) +

  ylim(-150,max(label_data$tot, na.rm=T)) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  coord_polar() +

  # Add labels on top of each bar
  geom_text(data=label_data, aes(x=id, y=tot+10, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=5, angle= label_data$angle, inherit.aes = FALSE ) +

  # Add base line information
  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,0,0), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)

@@

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 5
nObsType <- nlevels(as.factor(data$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char)*nObsType, ncol(data)) )
colnames(to_add) <- colnames(data)
to_add$group <- rep(levels(Char), each=empty_bar*nObsType)
# to_add$individual <- rep(letters[1:6], each=empty_bar*nObsType)
data <- bind_rows(data, to_add)
data <- data %>% arrange(group, individual) %>% rowwise() %>%  mutate(id = as.numeric(as.factor(individual)))
data$id <- as.numeric(as.factor(data$individual))

# Get the name and the y position of each label
label_data <- data %>% group_by(id, individual) %>% summarize(tot=sum(value))
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)

# prepare a data frame for base lines
base_data <-  data %>% 
  group_by(group) %>% 
  summarize(start=min(id,na.rm=T), 
            end=max(id,na.rm=T) - empty_bar) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

@@

data <- data %>% 
  ungroup() %>% 
  mutate(individual = ifelse(is.na(observation),NA,observation))

ggplot(data) + 
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=observation,group=group), stat="identity", alpha=0.5) +
  scale_fill_manual("Catch Trend",
                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
                               wes_palette(n = 1, name = "Darjeeling2")
                    ),
                    na.value = "white"
  ) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 150, xend = start, yend = 150), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 200, xend = start, yend = 200), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +

  # Add text showing the value of each 100/75/50/25 lines
  ggplot2::annotate("text", x = rep(max(data$id),5), y = c(0, 50, 100, 150, 200), label = c("0", "50", "100", "150", "200") , color="grey", size=6 , angle=0, fontface="bold", hjust=1) +

  ylim(-150,max(label_data$tot, na.rm=T)) +
  theme_minimal() +
  theme(
    legend.position = "right",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  coord_polar() +

  # Add labels on top of each bar
  geom_text(data=label_data, aes(x=id, y=max(tot,na.rm=T), label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=2, angle= label_data$angle, inherit.aes = FALSE ) +

  # Add base line information
  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,1,0,0,0), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)

#### END COPY PASTE

empty_bar <- 5
nObsType <- nlevels(as.factor(Status_Data_Plot$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char)*nObsType, ncol(Status_Data_Plot)) )
colnames(to_add) <- colnames(Status_Data_Plot)
to_add$group <- rep(levels(Char), each=empty_bar*nObsType)
Status_Data_Plot <- bind_rows(Status_Data_Plot, to_add)
Status_Data_Plot <- Status_Data_Plot %>% arrange(group, individual)
# Status_Data_Plot$id <- c(rep(seq(1,round(nrow(Status_Data_Plot)/nObsType)) , each=nObsType),128)
Status_Data_Plot$id <- as.numeric(as.factor(Status_Data_Plot$individual))

# Top n of each group label
Top_Countries <- Status_Data_Plot %>% 
  group_by(group) %>% 
  top_n(5,value)

# Create labels for all but top 5
# Get the name and the y position of each label

label_data <- Status_Data_Plot %>% 
  group_by(id, individual) %>% 
  summarize(tot=sum(value))

label_data <- Status_Data_Plot 
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)

# prepare a data frame for base lines
base_data <- Status_Data_Plot %>% 
  group_by(group) %>% 
  summarize(start=min(id,na.rm=T), 
            end=max(id,na.rm=T) - empty_bar, 
            median = median(value, na.rm = T)
            ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data <- base_data
grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
grid_data$start <- grid_data$start - 1
# grid_data[1,2] <- 5 # Manually include Africa for the median
# grid_data[1,3] <- 1

# Global Variables
Seq_axis <- seq(0,100,20)
Plot_Limit <- max(Status_Data_Plot$value,na.rm=T)
Plot_Limit_Low <- -50
Ticks_Color <- "grey50"

ggplot(Status_Data_Plot) +

  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=observation), stat="identity", alpha=0.5) +
  # scale_fill_viridis(discrete=TRUE) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 150, xend = start, yend = 150), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 200, xend = start, yend = 200), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +

  # Add text showing the value of each 100/75/50/25 lines
  ggplot2::annotate("text", x = rep(max(Status_Data_Plot$id,na.rm=T),5), y = c(0, 50, 100, 150, 200), label = c("0", "50", "100", "150", "200") , color="grey", size=6 , angle=0, fontface="bold", hjust=1) +

  ylim(-150,max(label_data$value, na.rm=T)) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  coord_polar() +

  # Add labels on top of each bar
  geom_text(data=label_data, aes(x=id, y=value+10, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=5, angle= label_data$angle, inherit.aes = FALSE ) +

  # Add base line information
  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,0,0,1,1), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)
ggplot(Status_Data_Plot,
           fill=observation)
               fill=observation),
  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "black", alpha=0, size=0.3 , inherit.aes = FALSE ) +
  # geom_segment(data=median_data,
  #              aes(x = end,
  #                  y = median,
  #                  xend = start+5, 
  #                  yend = median,
  #                  colour = group),
  #              alpha=1,
  #              size=0.5 , 
  #              inherit.aes = FALSE ) +
           x = rep(max(Status_Data_Plot$id),length(Seq_axis)),
  ylim(-150,max(label_data$value, na.rm=T)) +
    legend.position = "none",
            aes(x=id,
                y=Plot_Limit,
  coord_polar()
    # legend.position = "",
                               wes_palette(n = 4, name = "Darjeeling2"),
                               "black","grey","blue"
                                 wes_palette(n = 4, name = "Darjeeling2"),
                                 "black","grey","blue"

@@

ggsave(
    plot = last_plot(),
    width = 12,
    height = 12,
    units = "in",
    filename = "Territory_circular_both.png",
    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
  )

>>>>

  # Get Variables to perform status metric
  Status_Data <- Data %>% 
    anti_join(No_Status_Data, # Removes no status data
              by = c("TaxonKey","Territory")
    ) %>% 
    # Get Max catch and max catch year
    group_by(TaxonKey,Territory) %>% 
    top_n(1,RMean) %>% 
    rename(Max_Peak = RMean,
           Y_Max_Peak = Year) %>% 
    # Get Min catch after peak catch
    left_join(Data,
              by = c("TaxonKey","Territory")
    ) %>% 
    filter(Year > Y_Max_Peak) %>% # Filter years after peak year
    group_by(TaxonKey,Territory) %>% 
    top_n(-1,RMean) %>% # find min value
    rename(Post_Max_Min = RMean,
           Y_Post_Max_Min = Year) %>% 
    left_join(Data,
              by = c("TaxonKey","Territory")
    ) %>% 
    # Final Species Status Evaluation 
    mutate(Status = ifelse(Year > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & ((RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50))),"Rebuilding",
                           ifelse((Year < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Year)),"Developing",
                                  ifelse(RMean > (Max_Peak*0.50),"Max Exploited",
                                         ifelse(Year > Y_Max_Peak & ((RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50))),"Over Exploited",
                                                ifelse(Year > Y_Max_Peak & RMean < (Max_Peak*0.10),"Collapsed",
                                                       "No Status")
                                         )
                                  )
                           )
    )) %>% 
    filter(Year > 2004) %>% # last 10 years of data
    group_by(TaxonKey,Territory,Status) %>% 
    summarise(n_Status= n()) %>% 
    group_by(TaxonKey,Territory) %>% 
    top_n(1,n_Status) %>%
    select(-n_Status)

@@

# Save data
write.csv(Species_Status,
          paste(Results_Path,"Species_Status.csv",sep=""),
                row.names = F)

@@

# Species list to get species names
Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/Species/exploited_species_list.csv",sep=""))
Spp_Clasification <- fread(paste(Data_Path,"Distribution_Data/Species/SppTaxonName.csv",sep=""))

@@

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(Data_Path,"Distribution_Data/Species_Status.csv", sep =""))
# Status_Data <- Species_Status

@@

length(unique(Total_trans_n$TaxonKey)) #633 spp at 100% and 25%

@@

# Countries_Data_Plot <- Tresholded_T_Data %>% 
#   group_by(Territory = CT_fishing_entity) %>% 
#   summarise(value = length(unique(TaxonKey))) %>% 
#   left_join(UN_Regions, by ="Territory") %>%
#   mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
#   rename(FishingRegion=Territory) %>% 
#   left_join(Clean_sau_eez_fes) %>% 
#   group_by(individual = fishing_entity,group) %>% 
#   summarise(Total_trans = sum(value,na.rm=T)) %>% 
#   mutate(value = ifelse(Total_trans > 100,100,Total_trans)) %>% 
#   filter(!is.na(individual)) %>% 
#   select(individual,group,value) %>% 
#   arrange(group,value)

@@

# Discrete_Data_Plot <- Tresholded_D_Data %>% 
#   summarise(value =sum(value,na.rm = T)*-1) %>% # Multyply them by -1 so they appear negative on plot
#   mutate(value = ifelse(value <= -100,-100,value)) %>% 
#   left_join(UN_Regions, by ="Territory") %>%
#   mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
#   filter(!is.na(Territory)) %>% 
#   select(individual = Territory,
#          group,
#          value)

@@

# Include possible missing countries in bothe datasets
# Countries_Data_Plot <- Discrete_Data_Plot %>% 
#   anti_join(Countries_Data_Plot,
#             by = c("individual","group")) %>% 
#   mutate(Total_Discrete = 0) %>% 
#   bind_rows(Countries_Data_Plot)

# Discrete_Data_Plot <- Countries_Data_Plot %>% 
#   anti_join(Discrete_Data_Plot,
#             by = c("individual","group")) %>% 
#   mutate(value = 0) %>% 
#   bind_rows(Discrete_Data_Plot)

@@

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(Status_Data_Plot$observation))
to_add <- data.frame(matrix(NA, empty_bar*nlevels(Char)*nObsType, ncol(Status_Data_Plot)) )
colnames(to_add) <- colnames(Status_Data_Plot)
to_add$group <- rep(levels(Char), each=empty_bar*nObsType)
to_add$value <- NA
to_add$observation <- NA
# to_add$individual <- to_add$group

data <- Status_Data_Plot %>% 
  bind_rows(to_add) %>% 
  ungroup() %>% 
  mutate(individual = forcats::fct_explicit_na(individual),
         group = forcats::fct_explicit_na(group)) %>%
  group_by(group,individual) %>% 
  mutate(id = as.integer(individual),
         order = as.integer(group))

# data$id <- as.integer(data$individual,na.rm=T)

# Get the name and the y position of each label
label_data <- data %>% 
  # filter(value > 0) %>% 
  group_by(id, individual) %>% 
  summarize(tot=sum(value,na.rm=T))

number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)

label_data <- label_data %>% 
  mutate(individual = ifelse(individual == "(Missing)",paste(" "),paste(individual)))

# prepare a data frame for base lines
base_data <-  data %>% 
  group_by(group) %>% 
  summarize(start=min(id,na.rm=T), 
            end=max(id,na.rm=T) - empty_bar,
            median = median(value, na.rm = T)) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

@@

data %>% 
  # filter(observation != "Np Status") %>% 
  ggplot() + 
  geom_bar(aes(x=id,
               y=value, 
               fill=observation),
           stat="identity", 
           alpha=0.5) +
  scale_fill_manual("Catch Trend",
                    values = c(
                      "#FF0000", # collapsed,
                      "#046C94", # Developing
                      "#00A08A", #Max exp.
                      "grey", #no status
                      "#F98400", #over exp
                      "#5BBCD6" # Rebuilding
                    ),
                    na.value = "white"
  ) +
  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "black", alpha=1, size=1 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), linetype = "dashed", colour = "grey", alpha=1, size=0.3, inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3, inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = -50, xend = start, yend = -50), linetype = "dashed", colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  # Add text showing the value of each 100/75/50/25 lines
  ggplot2::annotate("text", 
                    # x = rep(max(data$id),3),
                    x =c(1,0.2,1,0.8),
                    y = c(-50, 0, 50, 100),
                    label = c("50","0", "50", "100") , 
                    color="black", 
                    size=5.5, 
                    angle=0, 
                    # fontface="bold",
                    hjust=1) +

  ylim(-100,101) +
  theme_minimal() +
  theme(
    legend.position = c(0.93,0.14),
    legend.key.size = unit(1,"cm"),
    legend.title = element_text(size = 16),
    legend.text = element_text(size = 14),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  # Add labels on top of each bar
  geom_text(data=label_data,
            aes(
              x = id,
              # x=reorder(id,order),
                # y=max(tot,na.rm=T),
                # y=tot +1,
                y = 101,
                label=individual,
                hjust=hjust),
            color="black",
            fontface="bold",
            alpha=1,
            size=3,
            angle= label_data$angle,
            inherit.aes = FALSE ) +
  coord_polar()

@@

ggsave(
    plot = last_plot(),
    width = 16,
    height = 14,
    units = "in",
    filename = "Territory_circular_status.png",
    path = Figures_Path
  )
